---
title: "DAA"
author: "Xianchi Zhang"
date: '2022-09-15'
output:
  pdf_document: default
  html_document: default
  word_document: default
---
Respiratory Rate
a. From the histogram plot, the main range of respiratory rates of chiledren from age 0-3 is
around 25-50. 


```{r, echo = FALSE, message=FALSE}
###setwd("~/Documents/Duke MIDS/First semester/ids 702")
library(stargazer)
tinytex::install_tinytex()
res <- read.csv('Respiratory.csv')
a <- hist(res$Rate, main = "Respiratory Rate For Children From 0-3y", xlab = "Rate")

```

```{r,echo = FALSE, message=FALSE}
reg_model <- lm(Rate ~ Age, data = res)
```
b. Rate = -0.70Age + 47.05
Rate = B1 * Age + B0 (Intercept) + error
c. Fit the model to data
```{r, echo = FALSE, message = FALSE}
stargazer(reg_model, title = "Reg Model for Rate and Age", type = "text")
```
d. From the results above, 
p-value: the p-value for the age is less than 0.05, so we conclude that the predictor of age is significant and can reject the null hypothesis (H0 = 0), if we increase 1 unit of age, the rate will decrease by -0.7; age and rate has linear association relationship. 
confidence interval: On average, with one unit increase in the age, the rate will decrease by -0.75 - -0.64 according to the 95% confidence level. 
R^2 value: The linear model explains that 47.58% of the variance of Rate is explained by Age in the linear model. The model doesn't fit the data set very well. 

```{r, echo=FALSE, message=FALSE}
CI<-confint(reg_model, level = 0.95)
stargazer(CI, title = "Confidence Intervals for Rate vs. Age", type = "text")
```
e. 1. From the first plot "Residuals vs Fitted", it shows the rate and age has the linearity, but not too strong. 
   2. From the second plot "Normal Q-Q", most of the points fall close to the line, but there does appear to be some points slight curving in the end of line. So the normality assumption seems invalid for the data set.  
   3. The spread for the third plot doesn't show the constant acrossing the fitted values, there appears to be less spread for smaller fitted values but more spread in the larger fitted values, so the data doesn't met for this equal variances requirement. 
   4. The last plot is for the independence of errors. Because there is no showing points outside in the cook's distance, so there is no influential point. 
Overall, for the data sets, the normality and constant variance of errors don't satisfy the requirements. 



```{r, echo=FALSE, message=FALSE}
plot(reg_model)
```


2. Airbnb practice
a. EDA, model fitting and assessment


```{r, echo=FALSE, message=FALSE}
airbnb <- read.table(file = "/Users/super_enbicycle/Documents/Duke MIDS/First semester/ids 702/Listings_QueenAnne.txt", header = TRUE)
airbnb$room_type<- factor(airbnb$room_type)
airbnb$host_is_superhost<- as.logical(airbnb$host_is_superhost)
airbnb$host_identity_verified<- as.logical(airbnb$host_identity_verified)
airbnb$host_is_superhost_int<- as.numeric(airbnb$host_is_superhost)
airbnb$host_identity_verified_int<- as.numeric(airbnb$host_identity_verified)
stargazer(airbnb, title = "Summary of the Airbnb Data ",digits = 4, type = "text")

```



Some simple plots analysis


```{r, echo=FALSE, message=FALSE}
plot(airbnb$price, airbnb$accommodates, main = "Price vs. Accommodates" )
```


```{r,echo=FALSE, message=FALSE}
plot(airbnb$price, airbnb$bathrooms, main = "Price vs.Bathrooms")
```
```{r,echo=FALSE, message=FALSE}
plot(airbnb$price, airbnb$bedrooms, main = "Price vs.Bedrooms")
```
```{r,echo=FALSE, message=FALSE}
plot(airbnb$price, airbnb$room_type, main = "Price vs. Room Type")
```


b. price = -15.61 + 2.332*host_is_superhost_int -14.76*host_identity_verified_int - 41.07*room_typePrivate room +170.40*room_typeShared room + 7.21*accommodates  + 88.21*bathrooms + 33.45*bedrooms
(note: host_is_superhost_int and host_identity_verified_int are dummy variables : 0 or 1, so we need to separate the discussion
room_type is a categorical variable so that I set it to the three different levels, we need to separate the discussion. The model sets "Entire home/apt"as a reference.)
Because the F-statstics is large and p-value is less than 0.05, so the model shows significant relationship between the price and predictors. But it's noticing that the host_is_superhost_int and host_identity_verified_int are not significant predictors because the p-values are less than 0.05. 

```{r,echo=FALSE, message=FALSE}
mlra <- lm(price~host_is_superhost_int+host_identity_verified_int+room_type+accommodates+bathrooms+bedrooms, data = airbnb)
stargazer(mlra, title = "Multiple Linear Regression Model for Price vs Predictors", type = "text")
```

Confidence Intervals: 
```{r, echo=FALSE, message=FALSE}
CI1<- confint(mlra, level = 0.95)
stargazer(CI1, title = "Confidence Intervals for Price vs Predictors", type = "text")
```

Test the Nested F test
```{r, echo=FALSE, message=FALSE}
summary(aov(mlra), type = "III")
```

c. 1. There are two predictors' p-values less than 0.05 and don't show significance in this model: host_is_superhost_int and host_identity_verified_int, it means that these two predictors don't have relationship to impact the change of price. 
   2. The model has large f-statistics small p-value which show that the total model is significant and show the significant relationship between price and predictors. 
   3. We need to separate the discussions because the host_is_superhost_int and host_identity_verified_int are dummy variables, room_type is a categorical variable. 
host_is_superhost_int: if the host is superhost while holding others equal, then the price will increase 2.33, if not, the price will not be impacted
host_identity_verified_int: if the host has verified the identity while holding other factors equal, then the price will decrease 14.78, then the price will not be impacted. 
room_type: if the room type is private room while holding others equal, the price will decrease 41.07, if the room type is shared room while other factors are equal, the price will increase 170.40, if the room type is Entire home/apt, the price will increase 211.47. 
   4. R^2 value: The multiple linear regression explains that 66.02% of the variance of Price is explained by predictors in the model. The model fits the data well. 




d. From the fourth plot, it shows two possible outliers (31,148)/leverage points(31,138)/influential points(31,138) because they have larger standardized residuals than 3, unusual x values and fall outside the Cook's distance 0f 0.5-1. 

```{r, echo=FALSE, message=FALSE}
plot(mlra)
```

Now remove the outliers/leverage points/influential points:

```{r, echo=FALSE, message=FALSE}
airbnb1 <- airbnb[-c(31, 138, 148),]

```
mlra1(adjusted values table) vs. mlra (original values table)
```{r, echo=FALSE, message=FALSE}
mlra1 <- lm(price~host_is_superhost_int+host_identity_verified_int+room_type+accommodates+bathrooms+bedrooms, data = airbnb1)
stargazer(mlra, mlra1, title = "Compared Original and Adjusted Multiple Linear Regression Model", type = "text")
```

So, when I remove these unusual values, the F-statistic becomes larger as 101.9 and shows that the model fits the data better. Although the p-value of host_is_superhost_int is still larger tha 0.05, the p-value becomes lower than previous value. The p-value of host_identity_verified_int becomes less than 0.05 and shows the significance for the response variables, which means will impact the changes of price. 

Let me plot the model again, the fourth plot shows that the values appears to be spread more and no values exceed Cook's distance. 

```{r, echo=FALSE, message=FALSE}
plot(mlra1)
```



e. Yes, the first one is that we can't infer the correlation between price with other predictors as a causation. 
The second one is the data set may not fit the model due to the lack of requirement of the assumptions, and there are also other factors we can continue to analyze besided the MLR, such as possible interactions. 





```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```





